---
title: "Assignment one for the course: Reproducible Research "
author: "TeokKK"
date: "Monday, January 12, 2015"
output: html_document
---


Read in the activity  monitor dataset and stored in data


```{r,echo=TRUE}
library(plyr)
data<-read.csv("activity.csv")

```

Histogram of the total number os steps taken per day:

```{r, echo=TRUE}
int<-data[!is.na(data$steps),c(1,2,3)]
dd<-ddply(int,.(date),summarize,sum=sum(steps))
hist(dd[,2],main="Histogram of Total Number of Steps with",xlab="Total Steps")

```

The mean and median steps taken per day are
```{r, echo=TRUE}
ddply(int,.(date),summarize,mean=mean(steps),median=median(steps))

```
time series plot
```{r, echo=TRUE}
dd2<-ddply(int,.(interval),summarize,mean=mean(steps))
plot(dd2,type="l",main="5-minute interval (x-axis) VS average number of steps taken")
```
Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r, echo=TRUE}
dd2[which.max(dd2[,2]),1]
```
Imputing missing values

alculate and report the total number of missing values in the dataset (i.e. the total number of rows with NAs:
```
{r, echo=TRUE}
sum(is.na(data$steps))
```
Replace the missing steps value by the same day mean value.
```{r, echo=TRUE}
mydata<-data
ll<-dim(data)

for(i in 1:ll[1])
{
  
  if(is.na(mydata[i,1]))
  {
    y<-mydata[i,3]
    mydata[i,1]<-(dd2[dd2$interval==y,2])
   
  }

}


```
Histogram of the total number os steps taken per day:

```{r, echo=TRUE}

dd4<-ddply(mydata,.(date),summarize,sum=sum(steps))
hist(dd4[,2],main="Histogram of Total Number of Steps with missing values filled",xlab="Total Steps")

```
The mean and median steps taken per day are
```{r, echo=TRUE}
ddply(mydata,.(date),summarize,mean=mean(steps),median=median(steps))

```
Convert date column to date format and add one more coloumn (week) to indicate whether is weekend or weekday

```{r, echo=TRUE}
mydata$date<-as.Date(mydata$date,"%Y-%m-%d")

mydata$week<-ifelse(weekdays(mydata$date)=="Sunday"| weekdays(mydata$date)=="Saturday" ,"weekend","weekday")
  ```
